raptr: Representative and Adequate Prioritisation Toolkit in R

### 2016-09-30 code/rmarkdown/article.Rmd
+ reference fixes + added kate temp files to gitignore
+ update r pkg refs

<!-- biodiversity processes are important -->
Prioritisations must capture the ecological and evolutionary processes that sustain biodiversity [@r3; @r255]. Ecological processes, such as predator-prey interactions, pollination, and decomposition, are required for biodiversity to persist over short time-scales. Typically, they operate over small geographic domains--with exceptions such as migration and refugial habitats--and can be preserved using suitably large planning units [@r446] that each contain a discrete unit of habitat [@r448]. On the other hand, evolutionary processes are required for biodiversity to persist over long time-scales, and they typically operate over large geographic domains. Protected areas must represent adaptive evolutionary processes to foster resilience against environmental change [eg. climate change; @r247]. Protected areas must also preserve neutral evolutionary processes [@r5; @r67; @r63], arising from restriction of gene flow between populations. They are important for maintaining genetic diversity, and avoiding inbreeding depression. In recent decades, a wealth of data relevant to evolutionary processes has become available to conservation planners [eg. bioclimatic, genetic, phylogenetic, and trait data; @r33; @r453; @r460]. This boom has resulted in significant progress towards evolutionary processes into conservation planning at the infra- and inter-specific level [eg. @r68; @r470; @r469]. Yet such data are rarely used to guide conservation planning [@r61]. This is perhaps in large part due to the fact that existing reserve selection tools focus on capturing either biodiversity patterns or processes--but not both.

<!-- parametrisation of biodiversity patterns and processes in conventional conservation planning tools -->
Existing conservation planning tools are generally not well-suited for representing intra-specific biodiversity patterns and processes. To preserve the biodiversity processes that underpin a given species, a prioritisation must capture a representative sample of each species. For instance, to preserve predator-prey interactions, a prioritisation must preserve individuals from each species in the same areas [@r471]. To preserve adaptive evolutionary processes, a prioritisation must preserve the adaptive landscape of each species--populations experiencing different selection pressures [@r63]. To preserve neutral evolutionary processes, a prioritisation must secure individuals descended from each of the genetic lineages that comprise each species [@r5]. Planning tools that focus on such biodiversity processes [eg. \texttt{Diversity}; @r203] are unable to accommodate species-specific targets to ensure that prioritisations secure biodiversity features. Similarly, planning tools that focus on biodiversity patterns [eg. \texttt{Marxan}] cannot easily accomodate biodiversity processes. Previous attempts to accommodate processes into multi-species conservation planning have partitioned species' ranges into different groups, for example at habitat discontinuities [e.g. @r2] as a pre-processing step to render a new set of "pseudo-species". However, this approach assumes that the biodiversity processes that operate across a species' range can be readily split into discrete units. Yet data on biodiversity processes is often continuous, hierarchical, and hyper-dimensional, and so often cannot be reduced to a few categories without significant information loss [@r218].

>>>>

<!-- biodiversity processes are important -->
Prioritisations must capture the ecological and evolutionary processes that sustain biodiversity [@r3; @r255]. Ecological processes, such as predator-prey interactions, pollination, and decomposition, are required for biodiversity to persist over short time-scales. Typically, they operate over small geographic domains--with exceptions such as migration and refugial habitats--and can be preserved using suitably large planning units [@r446] that each contain a discrete unit of habitat [@r448]. On the other hand, evolutionary processes are required for biodiversity to persist over long time-scales, and they typically operate over large geographic domains. Protected areas must represent adaptive evolutionary processes to foster resilience against environmental change [eg. climate change; @r247]. Protected areas must also preserve neutral evolutionary processes [@r5; @r67; @r63], arising from restriction of gene flow between populations. They are important for maintaining genetic diversity, and avoiding inbreeding depression. In recent decades, a wealth of data relevant to evolutionary processes has become available to conservation planners [eg. bioclimatic, genetic, phylogenetic, and trait data; @r33; @r460; @r453]. This boom has resulted in significant progress towards evolutionary processes into conservation planning at the infra- and inter-specific level [eg. @r68; @r470; @r469]. Yet such data are rarely used to guide conservation planning [@r61]. This is perhaps in large part due to the fact that existing reserve selection tools focus on capturing either biodiversity patterns or processes--but not both.

<!-- parametrisation of biodiversity patterns and processes in conventional conservation planning tools -->
Existing conservation planning tools are generally not well-suited for representing intra-specific biodiversity patterns and processes. To preserve the biodiversity processes that underpin a given species, a prioritisation must capture a representative sample of each species. For instance, to preserve predator-prey interactions, a prioritisation must preserve individuals from each species in the same areas [@r471]. To preserve adaptive evolutionary processes, a prioritisation must preserve the adaptive landscape of each species--populations experiencing different selection pressures [@r63]. To preserve neutral evolutionary processes, a prioritisation must secure individuals descended from each of the genetic lineages that comprise each species [@r5]. Planning tools that focus on such biodiversity processes [eg. \texttt{Diversity}; @r203] are unable to accommodate species-specific targets to ensure that prioritisations secure biodiversity features. Similarly, planning tools that focus on biodiversity patterns (eg. \texttt{Marxan}) cannot easily accomodate biodiversity processes. Previous attempts to accommodate processes into multi-species conservation planning have partitioned species' ranges into different groups, for example at habitat discontinuities [e.g. @r2] as a pre-processing step to render a new set of "pseudo-species". However, this approach assumes that the biodiversity processes that operate across a species' range can be readily split into discrete units. Yet data on biodiversity processes is often continuous, hierarchical, and hyper-dimensional, and so often cannot be reduced to a few categories without significant information loss [@r218].
